\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-11 podc16/paper2.tex
typo in section on dependency-set algo

An example of implementation of such an algorithm is depicted by the pseudocode of \Cref{fig:deps-set-algo}. The idea is to let every process broadcast $c$ to all the processes in the system, in order to announce $c$. Then whenever a process $p$ receives $c$, it replies to the sender with the set $\mathcal{D}$ of commands that $p$ has observed so far, and such that $c$ and any command in $\mathcal{D}$ are \textit{non-commutative}. Afterwards, the process announcing $c$ collects the sets $\mathcal{D}$ for $c$ from a quorum of $\mathcal{Q}$ processes, and it locally suggests the union of those sets as final dependency-set for $c$.

The provided implementation satisfies the two properties of a dependency-set algorithm for the following reasons. Since any command in a dependency-set that is suggested by a process must be in the set $cmds_q$ of the commands received by some process $q$, and a process receives a command if and only if there exists some process that previously announced the command, then it follows that any command in any suggested dependency-set has been previously announced.

>>>>

An example of implementation of such an algorithm is depicted by the pseudocode of \Cref{fig:deps-set-algo}. The idea is to let every process broadcast $c$ to all the processes in the system, in order to announce $c$. Then whenever a process $p$ receives $c$, it replies to the sender with the set $\mathcal{D}$ of commands that $p$ has observed so far, and such that $c$ and any command in $\mathcal{D}$ do not commute. Afterwards, the process announcing $c$ collects the sets $\mathcal{D}$ for $c$ from a quorum of $\mathcal{Q}$ processes, and it locally suggests the union of those sets as final dependency-set for $c$.

The provided implementation satisfies the specification of a dependency-set algorithm for the following reasons. Since any command in a dependency-set that is suggested by a process must be in the set $cmds_q$ of the commands received by some process $q$, and a process receives a command if and only if there exists some process that previously announced the command, then it follows that any command in any suggested dependency-set has been previously announced.
